Classless Java

### 2015-10-04 paper/sections/Formalization.tex
Translation.

@@

\haoyuan{
I found this from the Internet. See Fig.~\ref{screenshot_png}.

An experiment. See Fig.~\ref{table_png}.
}

@@

>>>>

\subsection{Translation Rules}

\[ \inferrule{
  \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{
  \methods \} \text{ OK }}
{ \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods \} \longmapsto \\
  \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods; \textsf{ofMethod}(C_0); \textsf{otherMethod}(C_0) \}
} \quad \textsc{(Translation)} \]

\haoyuan{Not $\{ \methods; ... \}$, actually. Should avoid duplication.}

@@

\haoyuan{
I found this from the Internet. See Fig.~\ref{screenshot_png}.
An experiment. See Fig.~\ref{table_png}.
}

@@

\subsubsection{Auxiliary function:???}

\begin{equation*}
\begin{array}{ll}
\textsf{ofMethod}(C_0) = ... & ... \\
\textsf{otherMethod}(C_0) = \methods_1; \methods_2; \methods_3 \hspace{0.1in} & \textsf{resolve}(C_0) = \overline{field} \\
& \method_1 = \textsf{setter}(field) \\
& \method_2 = \textsf{with}(field) \\
& \method_3 = \textsf{clone}(field) \\
\textsf{resolve}(C_0) = \overline{field} & \mif\ \textsf{methods}(C_0) = \mhs \\
& \forall field^{\mh} \in \overline{field}, \mh \in \mhs, \textsf{isField}(\mBody(\mh, C_0)) = \QM{true} \\
& \forall \mh \in \mhs, \mh \textsf{ isField or isSetter or isWith or isClone or isDefault} \\
\textsf{methods}(C_0) = \mhs\ \bigcup\ \overline{\textsf{methods}(C)} & \mif\ \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \} \\
& \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \} \\
\textsf{isField}(\method) = \QM{true} & \mif\ \method = T\ m();\ T \ne \QM{void} \\
\textsf{setter}(field) = \none & \mif\ field^\mh = T\ m(),\ field^{setter} = \QM{void} \\
\textsf{setter}(field) = T_0\ \QM{set}m(T\ x); & \mif\ field^\mh = T\ m(),\ field^{setter} = T_0 \\
\textsf{with}(field) = \none & \mif\ field^\mh = T\ m(),\ field^{with} = \none \\
\textsf{with}(field) = T_0\ \QM{with}m(T\ x); & \mif\ field^\mh = T\ m(),\ field^{with} = T_0 \\
\textsf{clone}(field) = T_0\ \QM{clone}(); & \mif\ field^\mh = T\ m(),\ field^{clone} = T_0
\end{array}
\end{equation*}

\haoyuan{Details? ThisReference? Assignment?}
